Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
fixed cog means table

# Loading in needed packages
library(tidyverse) #install.packages("tidyverse")
library(rio) #install.packages("rio")
library(gt) #install.packages("gt")
library(reshape2) #install.packages("reshape2")
library(ggcorrplot) #install.packages("ggcorrplot")
library(patchwork) #install.packages("patchwork")
library(janitor) #install.packages("janitor")
library(fs) #install.packages("fs")
library(furniture) #install.packages("furniture")
library(caret) #install.packages("caret")
library(effectsize) #install.packages("effectsize")
library(parameters) #install.packages("parameters")
library(performance) #install.packages("performance")
library(bayestestR) #install.packages("bayestestR)
library(rstanarm) #install.packages("rstanarm")

@@

@@

@@

## Hearing Threshold

>>>>

# Loading in needed packages
library(tidyverse) #install.packages("tidyverse")
library(rio) #install.packages("rio")
library(gt) #install.packages("gt")
library(gtsummary) #install.packages("gtsummary")
library(reshape2) #install.packages("reshape2")
library(ggcorrplot) #install.packages("ggcorrplot")
library(patchwork) #install.packages("patchwork")
library(janitor) #install.packages("janitor")
library(fs) #install.packages("fs")
library(furniture) #install.packages("furniture")
library(caret) #install.packages("caret")
library(effectsize) #install.packages("effectsize")
library(parameters) #install.packages("parameters")
library(performance) #install.packages("performance")
library(bayestestR) #install.packages("bayestestR)
library(rstanarm) #install.packages("rstanarm")

# Load in dataset

demo <- rio::import("participant_demo.csv")

data <- rio::import("cleaned_data.csv")

@@

# Calculating pretest and posttest intelligibility for the listeners
pl_int <- data %>%
  dplyr::group_by(id, speaker, type) %>%
  dplyr::mutate(pwc = (sum(correct_words)/sum(target_number))*100,
                best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
  dplyr::summarize(mean_pwc = mean(pwc, na.rm = T),
                   across(c(contains("_c"), contains("_u"), contains("win")),
                          ~first(.x)
                          )) %>%
  dplyr::ungroup()

# Subsetting age from demo df

age <- demo %>%
  select(id, age)

# Merging listener age into pl_int

pl_int <- dplyr::left_join(age, pl_int, by = "id")

@@

## Participant Demographics

TBD

@@

int_table <- pl_int %>%
  dplyr::filter(type == "pretest") %>%
  dplyr::select(id, speaker, age, ends_with("_c"), best_win) %>%
  dplyr::select(-fluid_cog_c) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  group_by(id, speaker) %>% 
  summarize(across(everything(), first)) %>% 
  ungroup() %>% 
  select(-id) %>% 
  tbl_summary(
    by = "speaker",
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

int_table

int_table %>%
  gt::gtsave("Tables/means_tabel.html")

# Intelligibiltiy Descriptives Table
